PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in of coping ocir, phq, gad, and pcl 2

```{r coping glad pcl cleaning}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base_numeric = pcl6.stressful_experience_repeated_images_numeric,
    pcl.stressful_experience_repeated_images_base = pcl6.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base_numeric = pcl6.stressful_experience_upset_reminded_numeric,
    pcl.stressful_experience_upset_reminded_base = pcl6.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_base_numeric = pcl6.avoiding_activities_stressful_experience_numeric, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl6.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base_numeric = pcl6.cut_people_feeling_distant_numeric,
    pcl.cut_people_feeling_distant_base = pcl6.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base_numeric = pcl6.feeling_irritable_or_having_angry_outbursts_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl6.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base_numeric = pcl6.difficulty_concentrating_numeric,
    pcl.difficulty_concentratin_base = pcl6.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro_numeric = pcl6.stressful_experience_repeated_images.1_numeric,
    pcl.stressful_experience_repeated_images_retro = pcl6.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro_numeric = pcl6.stressful_experience_upset_reminded.1_numeric,
    pcl.stressful_experience_upset_reminded_retro = pcl6.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro_numeric = pcl6.avoiding_activities_stressful_experience.1_numeric,
    pcl.stressful_situation_avoiding_activities_retro = pcl6.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro_numeric = pcl6.cut_people_feeling_distant.1_numeric,
    pcl.cut_people_feeling_distant_retro = pcl6.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric = pcl6.feeling_irritable_or_having_angry_outbursts.1_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl6.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro_numeric = pcl6.difficulty_concentrating.1_numeric,
    pcl.difficulty_concentrating_retro = pcl6.difficulty_concentrating.1
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping glad phq cleaning}
coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    phq.little_interest_or_pleasure_in_doing_things_retro = phq9.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq9.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq9.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq9.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq9.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq9.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq9.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq9.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro = phq9.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_retro_numeric = phq9.little_interest_or_pleasure_in_doing_things_numeric,
    phq.feeling_down_depressed_or_hopeless_retro_numeric = phq9.feeling_down_depressed_or_hopeless_numeric,
    phq.staying_asleep_sleeping_trouble_retro_numeric = phq9.staying_asleep_sleeping_trouble_numeric,
    phq.feeling_tired_or_having_little_energy_retro_numeric = phq9.feeling_tired_or_having_little_energy_numeric,
    phq.poor_appetite_or_overeating_retro_numeric = phq9.poor_appetite_or_overeating_numeric,
    phq.feeling_bad_failure_family_retro_numeric = phq9.feeling_bad_failure_family_numeric,
    phq.trouble_concentrating_reading_newspaper_retro_numeric = phq9.trouble_concentrating_newspaper_reading_numeric, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro_numeric = phq9.moving_fidgety_opposite_slowly_numeric, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro_numeric = phq9.dead_hurting_thoughts_numeric,
    phq.little_interest_or_pleasure_in_doing_things_base = phq9.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq9.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq9.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq9.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq9.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq9.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq9.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq9.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base = phq9.dead_hurting_thoughts.1,
    phq.little_interest_or_pleasure_in_doing_things_base_numeric = phq9.little_interest_or_pleasure_in_doing_things.1_numeric,
    phq.feeling_down_depressed_or_hopeless_base_numeric = phq9.feeling_down_depressed_or_hopeless.1_numeric,
    phq.staying_asleep_sleeping_trouble_base_numeric = phq9.staying_asleep_sleeping_trouble.1_numeric,
    phq.feeling_tired_or_having_little_energy_base_numeric = phq9.feeling_tired_or_having_little_energy.1_numeric,
    phq.poor_appetite_or_overeating_base_numeric = phq9.poor_appetite_or_overeating.1_numeric,
    phq.feeling_bad_failure_family_base_numeric = phq9.feeling_bad_failure_family.1_numeric,
    phq.trouble_concentrating_reading_newspaper_base_numeric = phq9.trouble_concentrating_newspaper_reading.1_numeric, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base_numeric = phq9.moving_fidgety_opposite_slowly.1_numeric, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base_numeric = phq9.dead_hurting_thoughts_numeric

@@

@@

>>>>

```{r coping glad pcl cleaning}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping glad phq cleaning}
coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care,
    phq.pandemic_felt_feelings,
    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

    ocir.felt_pandemic_feelings,

@@

  add_numeric(., exclude = exclude_cols) %>%
